The Name of the Title is Hope

### 2023-09-15 input/1_teaser_figure.tex
Updates from Overleaf

\begin{teaserfigure}
  \includegraphics[width=\textwidth]{tex_sample_files/sampleteaser.pdf}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

>>>>

\begin{teaserfigure}
  \includegraphics[width=\textwidth]{figures/task_design.png}
  \caption{(a) description of the experimental conditions, (b) their hypothesized effects on sense of agency from the perspective of a comparator model, is inspired by~\citet{Dewey2019-dg} (c) depicts the flow of movement generation in the participant and the system between conditions.}
  \Description{(a) description of the experimental conditions, (b) their hypothesized effects on sense of agency from the perspective of a comparator model, is inspired by~\citet{Dewey2019-dg} (c) depicts the flow of movement generation in the participant and the system between conditions.}
  \label{fig:teaser}
\end{teaserfigure}

### 2023-09-15 input/2_introduction.tex
Updates from Overleaf

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw}. However, augmented users often report dissociative experiences, frequently disrupting their sense of agency (SoA)~\citep{Gilbert2017-ze, Gilbert2019-uc}.

@@

\subsection{Preserving Agency using Brain Signals of the Intent to (Inter-) act}
% 4. (long) Anwser with teaser image
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
In this paper, we present a bleeding edge prototype to challenge the disruption in experiencing agency during action augmentation. We developed a brain-computer interface (BCI) that establishes a fast communication channel between a user's brain signals and a physical end effector. The  INTENTION system controls the user's muscles at the time of their \textit{intent to interact}, as measured through readiness potentials (RP) manifesting in the user's electroencephalogram (EEG)~\cite{Nguyen2023-me, Schurger2021-vp, Schultze-Kraft2016-bx, Schultze-Kraft2021-cu}.

>>>>

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw, Kunze2017-co}. However, augmented users often report dissociative experiences, frequently disrupting their sense of agency (SoA)~\citep{Gilbert2017-ze, Gilbert2019-uc}.

@@

\subsection{Preserving Agency using Brain Signals of the Intent to (Inter-) act}
% 4. (long) Anwser with teaser image
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
In this paper, we present a bleeding edge prototype to challenge the disruption in experiencing agency during action augmentation. We developed a brain-computer interface (BCI) that establishes a fast communication channel between a user's brain signals and a physical end effector. The AUGMENTATION system (from hereon referred to simply as \textit{system}) controls the user's muscles at the time of their \textit{intent to interact}, as measured through readiness potentials (RP) manifesting in the user's electroencephalogram (EEG)~\cite{Nguyen2023-me, Schurger2021-vp, Schultze-Kraft2016-bx, Schultze-Kraft2021-cu}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/bci_game.png}
    \caption{Our Augmentation system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's EEG signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, the user's hand is moved by trigger electrical muscle stimulation (EMS). Image presented with consent from participant.}
\end{figure}

### 2023-09-15 input/3_related_work.tex
Updates from Overleaf

In the simple case of pressing a key on a piano, the finger movement is constantly compared to the predicted proprioceptive feedback. Subsequently, the tone generated by the key press is evaluated against auditory predictions. On a semantic level, these predictions may be in reference to whether the tone loudness corresponds to the velocity of the key press or whether the tone is in-key or out-of-key~\cite{Pangratz2023-ew}. If these predictions -- based on the intended movement and its expected outcome -- explain the sensory data available, agency is experienced (see figure~\ref{fig:task_design} BASELINE).

@@

As opposed to intended actions using our own body, movement augmentation hardware allows moving a user's body without their intention. Today, there are three main technologies to physically augment users' actions: Through the use of mechanical actuators, i.e. exoskeletons, a user's body can be moved by applying forces to the extremities. Another possibility is to stimulate the brain directly, so the stimulation causes a motor response, for example by using transcranial magnetic stimulation (TMS). Lastly, electrical muscle stimulation (EMS) makes the user's extremities move by sending current into their muscle activating nerves. In these scenarios, the user computes no predictions about the movement and its outcome. Thus, in reference to the comparator model, none or a decreased SoA arises in the case of externally controlled actions, for example by brain stimulation~\cite{Haggard2002-sz} or when the body is moved by another person~\cite{Kuhn2013-ls}. With something or somebody else moving our body to perform, e.g., a keypress on a piano, the lack of intention to play the piano -- and derived sensory and semantic predictions -- impacts the experience of agency. Such involuntary movements may even cause adverse effects: In case a body movement is elicited by TMS simulation, a resistance to the movement may manifest~\cite{Haggard2002-sz} (see figure~\ref{fig:task_design} NO INTENTION)

@@

In the present study, we leveraged the RP in a similar way, i.e. to discriminate between two \textit{action} states as the basis to trigger an action augmentation device or not. The technology we used with our prototype, electrical muscle stimulation (EMS), sends currents to the user's forearm leading to a contraction of the flexor muscle moving the ring finger as an augmented movement.

>>>>

In the simple case of pressing a key on a piano, the finger movement is constantly compared to the predicted proprioceptive feedback. Subsequently, the tone generated by the key press is evaluated against auditory predictions. On a semantic level, these predictions may be in reference to whether the tone loudness corresponds to the velocity of the key press or whether the tone is in-key or out-of-key~\cite{Pangratz2023-ew}. If these predictions -- based on the intended movement and its expected outcome -- explain the sensory data available, agency is experienced.
% (see figure~\ref{fig:task_design} INTENTION).

@@

As opposed to intended actions using our own body, movement augmentation hardware allows moving a user's body without their intention. Today, there are three main technologies to physically augment users' actions: Through the use of mechanical actuators, i.e. exoskeletons, a user's body can be moved by applying forces to the extremities. Another possibility is to stimulate the brain directly, so the stimulation causes a motor response, for example by using transcranial magnetic stimulation (TMS). Lastly, electrical muscle stimulation (EMS) makes the user's extremities move by sending current into their muscle-activating nerves. In these scenarios, the user computes no predictions about the movement and its outcome. Thus, in reference to the comparator model, none or a decreased SoA arises in the case of externally controlled actions, for example by brain stimulation~\cite{Haggard2002-sz} or when the body is moved by another person~\cite{Kuhn2013-ls}. With something or somebody else moving our body to perform, e.g., a key press on a piano, the lack of intention to play the piano -- and derived sensory and semantic predictions -- impacts the experience of agency. Such involuntary movements may even cause adverse effects: In case a body movement is elicited by TMS simulation, a resistance to the movement may manifest~\cite{Haggard2002-sz}.
% (see figure~\ref{fig:task_design} EXTERNAL CONTROL)

@@

In the present study, we leveraged the RP in a similar way, i.e. to discriminate between two \textit{action} states as the basis to trigger an action augmentation device or not. The technology we used with our system, electrical muscle stimulation (EMS), sends currents to the user's forearm leading to a contraction of the flexor muscle moving the ring finger as an augmented movement.

### 2023-09-15 input/5_user_study_and_methods.tex
Updates from Overleaf

\subsection{Experimental Task, Design and Procedure}
Participants performed a simple tapping task in three conditions with 75 trials each: BASELINE, NO INTENTION (to move) and INTENTION (to move) EMS, see figure~\ref{fig:task_design}.

\indent\textbf{BASELINE.} The task went as follows: (1) a fixation cross appeared on a tablet screen and participants were instructed to rest and wait until it disappeared; (2) then, they were instructed to wait for a brief moment (2 to 3s), before (3) initiating their movement and tap the screen. In line with the literature on the origin of the RP generating process they were told ``to avoid pre-planning the movement, avoid any obvious rhythm over trials, and to press when they felt the spontaneous urge to move''~\cite{Schultze-Kraft2021-cu}. (4) After the screen was tapped, a tone was played at a pseudo-random delay of 200, 350, or 500ms. Participants were now asked to estimate the delay, typing in their answer on a number pad of an attached keyboard. After confirming their answer by hitting the return key, the next trial started.
During BASELINE, participants were equipped with Electromyogram (EMG) sensors instead of EMS electrodes. BASELINE data was used as training data for the BCI, see section~\ref{BCI} below, as well as to select stereotypical reaction times in the NO INTENTION condition.

\indent\textbf{NO INTENTION.} The task structure was identical to BASELINE, however, participants were now instructed to hold and wait for the muscle stimulation to move their finger thereby eliciting the screen tap. The timing for the EMS trigger was taken by randomly choosing a time between the 5th and 95th percentile of their actual individual reaction time in the BASELINE condition.

\indent\textbf{INTENTION.} The task and instruction were identical to BASELINE with one additional instruction: ``you will now work \textit{with} the system''. During INTENTION, the muscle stimulation hardware was controlled by the BCI. The classifier was set to active after the fixation cross disappeared and until a screen tap was registered. Hence, the muscle was not stimulated at other times during a trial, so as not to interfere with participants typing in their time estimation response.

The order of the conditions was not pseudo-randomized since training data obtained in BASELINE was required for both NO INTENTION and INTENTION. Furthermore, INTENTION was always the last condition, thereby allowing for a prolonged interview.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/task_design.png}
    \caption{(a) description of the experimental conditions, (b) their hypothesized effects on sense of agency from the perspective of a comparator model, is inspired by~\citet{Dewey2019-dg} (c) depicts the flow of movement generation in the participant and the system between conditions.}
    \label{fig:task_design}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/task_progression.png}
    \caption{Visualization of task progression}
    \label{fig:progression}
\end{figure}

\subsection{Apparatus}
The experimental setup, depicted in Figure~\ref{}, comprised: (1) a 1-channel EMG device, (2) a 64-channel EEG system, (3) a medically-compliant EMS device connected via two electrodes worn on the forearm, and (4) a tablet to run the experiment and collect behavioral responses. To assist readers in replicating our experiment, we provide the necessary technical details, the complete source code for the experiment, the collected data, and the analysis scripts\footnote{[anonymized]}.
% TODO add links after anonymization is lifted.

@@

\indent\textbf{(3) Electrical Muscle Stimulation.} We actuated the ring finger via EMS, which was delivered with two electrodes attached to the participants' flexor digitorum profundus muscle. We utilized the flexor digitorum profundus since we found that we can robustly actuate it without inducing unintended motion of neighboring fingers. This finger actuation was achieved via a medically-compliant battery powered muscle stimulator (TENS/EMS Super Duo Plus, prorelax, Düren, Germany). The EMS system's output was controlled by flipping a solid state relay (silent) connected via an Arduino Uno (Arduino, Monza, Italy) to the experiment computer. The EMS was pre-calibrated by the participant to ensure a pain-free but effective stimulation and robust actuation leading to an `immediate' tap on the touchscreen after actuation. To ensure a comfortable experimental experience so that participants relaxed their arm musculature as much as possible, a custom built hand rest (support device) was placed on top of the touchscreen for participants, see figure ~\ref{fig:task_design} c.
% [todo] What were the settings of the stimulation?

@@

% alternative headings:
% Brain-Computer Interface to Detect EEG Readiness Potentials }
% Classifiying EEG Signals of the Intent to Interact
\subsection{Brain-Computer Interface}\label{BCI}
The data obtained in BASELINE was used to train the BCI. We utilized the [anonymized] and the EEGLAB~\cite{Delorme2004-sn} toolbox inside the MATLAB (The MathWorks Inc. Natick, MA, USA) environment for preprocessing both EEG and EMG data. First, to generate behavioral labels at a high temporal resolution for the EEG-based classifier, we leveraged EMG data from the flexor digitorum profundus. EMG amplitudes were band-pass filtered from 20 to 100 Hz and subsequently squared. Next, in order to label the time of movement onset, the EMG data was averaged across trials for the second preceding the screen tap. From this averaged data, the first sample where the EMG amplitude exceeded the 95th percentile was selected as the time of movement onset.
% bemobil pipeline

@@

\subsubsection{Preprocessing EEG and Selecting discriminative channels}
The EEG data was band pass filtered from 0.1 to 15 Hz. In the first step to prepare the EEG data for classification, noisy data segments were rejected. To this end, the EEGLAB function `autorej' was used, keeping default parameters. A trial was excluded if \textit{either} data from the \textit{idle} or \textit{pre-movement} class was rejected.

@@

\subsection{Measures of Agency Experience: Intentional Binding, Question \& Interview}
To assess if SoA was preserved, an intentional binding measure, a standardized question, and an interview following the movement INTENTION block were investigated. At the conclusion of each condition we prompted participants to rate their experienced agency on a 7-point Likert scale with the statement ``It felt like I was in control of the movements during the task.'', the item was copied from~\cite{Hornbaek}. Following INTENTION we interviewed users about their experience working with the EMS BCI. After prompting users to recall their experience and summarize what their task had been we set the focus to the tapping movement and asked them to ignore the time estimation task for the following questions. We entered the open part of the interview by asking: ``What did the system do?'' followed up by ``What was the difference between the three conditions''. After some time, and depending on their answers, we reset the focus to the INTENTION condition and asked ``How often was the system active?'' followed by ``What do you think caused the actions of the system?''. This was then followed up by an `open' interview in which we frequently asked `how' and `why' questions to inquire about the user's experience.

% add back in after anonymization: All interviews were manually transcribed and then automatically translated using DeepL\footnote{https://www.deepl.com/translator}
We analyzed the interviews that always followed the INTENTION condition by loosely following~\citet{Mayring2015-pp}. All interviews were manually transcribed and [anonymized]. Prior to screening the texts, two experts clustered the responses into 3 clusters: First, ``Functionality'' referred to what participants attributed the source of the stimulation. Next, we clustered responses according to ``Guessed percentage'' of correct interaction, i.e. participants estimate of how well the system was aligned with their intention. For the cluster ``Correct Interaction'', we specifically queried participants to recall the moments where the stimulation felt in line with their intention to move, then we clustered their responses into positive and negative valence sentiments.

@@

In line with the literature on intentional binding, we hypothesized that for both BASELINE and INTENTION conditions the time intervals should be underestimated. This should not be the case for the augmented NO INTENTION condition where users had no intention to move. Hence, when binding occurs, the intervals should be underestimated, hinting at a higher SoA. To test this, we fit a linear mixed effects model with \textit{condition} (BASELINE, NO INTENTION, INTENTION) as a fixed effect. As a random effect, we considered the intercepts for participants. We obtained p-values of the coefficients by calculating likelihood-ratio tests~\cite{winterLinearModelsLinear2013}. All parameters were estimated by maximum likelihood estimation~\cite[see][]{Pinheiro2000}. Post-hoc, pairwise contrasts were computed using estimated marginal means with Tukey's methods for multiple comparisons corrections~\cite{Lenth2020-xk}.

Next, we hypothesized that subjective ratings of control over the tap movement are comparable between BASELINE and INTENTION and lower in the NO INTENTION condition. Again, we fit a linear mixed effects model with \textit{condition} as a fixed effect and participant ID as a random effect. Coefficients were assessed in the same way as for the intentional binding parameter above.

In short, we tested two main hypotheses with regard to experiencing agency in our three experimental conditions: (1) participants underestimate the tone delay when acting intentionally. Adding EMS in line with participants' intention to move does not affect this underestimation. (2) The subjective feeling of control is comparable between BASELINE and INTENTION conditions. NO INTENTION should decrease the feeling of control significantly. Additionally, we report the clustered interviews anecdotally.

>>>>

\subsection{Experimental Task, Design and Procedure}
Participants performed a simple tapping task in three conditions with 75 trials each: INTENTION, EXTERNAL, and AUGMENTED, see figure~\ref{fig:task_design}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/task_new.pdf}
    \caption{Interaction flow depicting one trial in our touchscreen tapping task.}
    \label{fig:progression}
\end{figure}

\indent\textbf{INTENTION.} The task went as follows: (1) a fixation cross appeared on a tablet screen and participants were instructed to rest and wait until it disappeared; (2) then, they were instructed to wait for a brief moment (2 to 3s), before (3) initiating their movement and tap the screen. In line with the literature on the origin of the RP generating process they were told ``to avoid pre-planning the movement, avoid any obvious rhythm over trials, and to press when they felt the spontaneous urge to move''~\cite{Schultze-Kraft2021-cu}. (4) After the screen was tapped, a tone was played at a pseudo-random delay of 200, 350, or 500ms. Participants were now asked to estimate the delay, typing in their answer on a number pad of an attached keyboard. After confirming their answer by hitting the return key, the next trial started.
During INTENTION, participants were equipped with Electromyogram (EMG) sensors instead of EMS electrodes. INTENTION data was used as training data for the BCI, see section~\ref{BCI} below, as well as to select stereotypical reaction times in the EXTERNAL condition.

\indent\textbf{EXTERNAL.} The task structure was identical to INTENTION, however, participants were now instructed to hold and wait for the muscle stimulation to move their finger thereby eliciting the screen tap. The timing for the EMS trigger was taken by randomly choosing a time between the 5th and 95th percentile of their actual individual reaction time in the INTENTION condition.

\indent\textbf{AUGMENTED.} The task and instruction were identical to INTENTION with one additional instruction: ``you will now work \textit{with} the system''. During AUGMENTED, the muscle stimulation hardware was controlled by the BCI. The classifier was set to active after the fixation cross disappeared and until a screen tap was registered. Hence, the muscle was not stimulated at other times during a trial, so as not to interfere with participants typing in their time estimation response.

The order of the conditions was not pseudo-randomized since training data obtained in INTENTION was required for both EXTERNAL and AUGMENTED. Furthermore, AUGMENTED was always the last condition, thereby allowing for a prolonged interview.

% \begin{figure*}
%     \centering
%     \includegraphics[width=\textwidth]{figures/task_design.png}
%     \caption{(a) description of the experimental conditions, (b) their hypothesized effects on sense of agency from the perspective of a comparator model, is inspired by~\citet{Dewey2019-dg} (c) depicts the flow of movement generation in the participant and the system between conditions.}
%     \label{fig:task_design}
% \end{figure*}

\subsection{Apparatus}
The experimental setup, depicted in Figure~\ref{fig:setup}, comprised: (1) a 1-channel EMG device, (2) a 64-channel EEG system, (3) a medically-compliant EMS device connected via two electrodes worn on the forearm, and (4) a tablet to run the experiment and collect behavioral responses. To assist readers in replicating our experiment, we provide the necessary technical details, the complete source code for the experiment, the collected data, and the analysis scripts\footnote{[anonymized]}.
% TODO add links after anonymization is lifted.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/setup.png}
    \label{fig:setup}
    \caption{Experimental setup of measurement-- and input devices (image with consent from participant).}
\end{figure}

\indent\textbf{(3) Electrical Muscle Stimulation.} We actuated the ring finger via EMS, which was delivered with two electrodes attached to the participants' flexor digitorum profundus muscle. We utilized the flexor digitorum profundus since we found that we can robustly actuate it without inducing unintended motion of neighboring fingers. This finger actuation was achieved via a medically-compliant battery powered muscle stimulator (TENS/EMS Super Duo Plus, prorelax, Düren, Germany). The EMS system's output was controlled by flipping a solid state relay (silent) connected via an Arduino Uno (Arduino, Monza, Italy) to the experiment computer. The EMS was pre-calibrated by the participant to ensure a pain-free but effective stimulation and robust actuation leading to an `immediate' tap on the touchscreen after actuation. To ensure a comfortable experimental experience so that participants relaxed their arm musculature as much as possible, a custom built hand rest (support device) was placed on top of the touchscreen for participants, see figure~\ref{fig:setup}.
% [todo] What were the settings of the stimulation?

@@

% alternative headings:
% Brain-Computer Interface to Detect EEG Readiness Potentials }
% Classifiying EEG Signals of the Intent to Interact
\subsection{Brain-Computer Interface}\label{BCI}
The data obtained in INTENTION was used to train the BCI. We utilized the [anonymized] and the EEGLAB~\cite{Delorme2004-sn} toolbox inside the MATLAB (The MathWorks Inc. Natick, MA, USA) environment for preprocessing both EEG and EMG data. First, to generate behavioral labels at a high temporal resolution for the EEG-based classifier, we leveraged EMG data from the flexor digitorum profundus. EMG amplitudes were band-pass filtered from 20 to 100 Hz and subsequently squared. Next, in order to label the time of movement onset, the EMG data was averaged across trials for the second preceding the screen tap. From this averaged data, the first sample where the EMG amplitude exceeded the 95th percentile was selected as the time of movement onset.
% bemobil pipeline

@@

\subsubsection{Preprocessing EEG and Selecting discriminative channels}\label{eeg_methods}
The EEG data was band pass filtered from 0.1 to 15 Hz. In the first step to prepare the EEG data for classification, noisy data segments were rejected. To this end, the EEGLAB function `autorej' was used, keeping default parameters. A trial was excluded if \textit{either} data from the \textit{idle} or \textit{pre-movement} class was rejected.

@@

\subsection{Measures of Agency Experience: Intentional Binding, Question \& Interview}
To assess if SoA was preserved, an intentional binding measure, a standardized question, and an interview following the AUGMENTED block were investigated. At the conclusion of each condition we prompted participants to rate their experienced agency on a 7-point Likert scale with the statement ``It felt like I was in control of the movements during the task.'', the item was copied from~\cite{Hornbaek}. Following AUGMENTED we interviewed users about their experience working with the system. After prompting users to recall their experience and summarize what their task had been we set the focus to the tapping movement and asked them to ignore the time estimation task for the following questions. We entered the open part of the interview by asking: ``What did the system do?'' followed up by ``What was the difference between the three conditions''. After some time, and depending on their answers, we reset the focus to the AUGMENTED condition and asked ``How often was the system active?'' followed by ``What do you think caused the actions of the system?''. This was then followed up by an `open' interview in which we frequently asked `how' and `why' questions to inquire about the user's experience.

% add back in after anonymization: All interviews were manually transcribed and then automatically translated using DeepL\footnote{https://www.deepl.com/translator}
We analyzed the interviews that always followed the AUGMENTED condition by loosely following~\citet{Mayring2015-pp}. All interviews were manually transcribed and [anonymized]. Prior to screening the texts, two experts clustered the responses into 3 clusters: First, ``Functionality'' referred to what participants attributed the source of the stimulation. Next, we clustered responses according to ``Guessed percentage'' of correct interaction, i.e., participants estimate of how well the system was aligned with their intention. For the cluster ``Correct Interaction'', we specifically queried participants to recall the moments where the stimulation felt in line with their intention to move, then we clustered their responses into positive and negative valence sentiments.

@@

In line with the literature on intentional binding, we hypothesized that the time intervals should be underestimated for the INTENTION and the AUGMENTED conditions. This should not be the case for the EXTERNAL condition where users had no intention to move. Hence, when binding occurs, the intervals should be underestimated, hinting at a higher SoA. To test this, we fit a linear mixed effects model with \textit{condition} (INTENTION, EXTERNAL, AUGMENTED) as a fixed effect. As a random effect, we considered the intercepts for participants. We obtained p-values of the coefficients by calculating likelihood-ratio tests~\cite{winterLinearModelsLinear2013}. All parameters were estimated by maximum likelihood estimation~\cite[see][]{Pinheiro2000}. Post-hoc, pairwise contrasts were computed using estimated marginal means with Tukey's methods for multiple comparisons corrections~\cite{Lenth2020-xk}.

Next, we hypothesized that subjective ratings of control over the tap movement are comparable between INTENTION and AUGMENTED and lower in the EXTERNAL condition. Again, we fit a linear mixed effects model with \textit{condition} as a fixed effect and participant ID as a random effect. Coefficients were assessed in the same way as for the intentional binding parameter above.

In short, we tested two main hypotheses with regard to experiencing agency in our three experimental conditions: (1) participants underestimate the tone delay when acting intentionally. Adding EMS in line with participants' intention to move does not affect this underestimation. (2) The subjective feeling of control is comparable between INTENTION and AUGMENTED conditions. EXTERNAL should decrease the feeling of control significantly. Additionally, we report the clustered interviews anecdotally.

### 2023-09-15 input/6_results.tex
Updates from Overleaf

\section{Results}
In the intentional binding task, i.e. the estimation of the time interval between tap and tone, participants generally underestimated the average real delay (350ms) in all three conditions (BASELINE M = 160.3, SD = 116; NO INTENTION M = 176.7, SD = 120.7, INTENTION M = 162.6, SD = 118.9). The condition influenced the estimation (${\chi^{2}_{(2)}} = 15.9, p < .001$). In NO INTENTION the estimation was higher compared to BASELINE (beta = 19.2, p < 0.001). Also in NO INTENTION, the estimation was higher compared to INTENTION (beta = 18.6, p < 0.001). No difference was observed between BASELINE and INTENTION.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/behavioral_results.png}
    \caption{Box-Whisker plots visualizing (a) the temporal binding effect over conditions. With an average presented time interval of 350ms, lower values in the estimated time interval indicate an underestimation, i.e., temporal binding. (b) visualizes the subjective ratings of control across conditions. Significance reportings refer to post-hocs test that followed a significant likelihood ratio test of the full model with condition as a factor against the model without it.}
    \label{fig:results}
\end{figure}

The subjective rating of control differed between conditions (${\chi^{2}_{(2)}} = 35.9, p < .001$). Post-hoc pairwise comparisons revealed that participants rated their motion control higher in BASELINE compared to NO INTENTION (beta = 4.9 , p < .0001) and BASELINE compared to INTENTION (beta = 3, p < .0001). Further, higher control was observed in INTENTION compared to NO INTENTION (beta = 1.9, p = .006).

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/EEG_results.pdf}
    \caption{![todo]: (a) depicts the grand average ERP at Cz comparing idle vs. movement intention with scalp map of voltage across all channels in the last [-100 0] interval of both idle and pre-move; B: What did the windows mean features look like. Boxplot with idle vs. pre-move and single observations, ROC -> in discussion mention that we want to do that continuously and not only look at the times preceding hand movement but at all time points}
    \label{fig:EEG_results}
\end{figure*}

@@

\subsection{Subjective Reports}
Six out of the eight participants made a reference to the source of the EMS in the INTENTION condition. In that subgroup, most participants wondered how the system worked, one remarked, ``I can't explain how it works technically.''. They found the stimulation to be sporadic, even during their own actions, leading to a belief that it was coincidental. As one participant put it, ``I have no idea what controlled the stimulation, I think it was coincidence when stimulation occurred.''. Furthermore, participants reported that they found the timing of the stimulation to be unpredictable, with one participant noting, ``Stimulation was random in time.''. Some perceived the stimulation as externally triggered, yet partially responsive to their choices, resulting in a sentiment captured by, ``I think that the stimulation in the third block was partly involuntary, but partly as if it was following my decision / choice.''. One participant briefly considered the involvement of their brain waves in controlling the stimulation, but expressing doubts about this possibility, stating, ``But I don't think that is the case.''.

Some participants reported that the stimulation ``sometimes overlapped with the movement, but not often,'' or, it ``came only rarely.'' Another one noted, ``In a few cases, the stimulation came when I had already started the movement.'' For several participants, this overlap between their actions and the system's response occurred infrequently, with another user noting, ``Once, in the millisecond range between my planned movement and its execution.'' However, for some participants, there were moments of near-perfect synchronization, as described by one participant, ``In 3 cases it happened that my intention to press and the impulse of the device happened simultaneously.'' Another one noted, ``Sometimes it really happened that they overlapped. So that I just started to move, and then the device activated,'' that user estimated an overlap of ``40\%'' while another said [we worked] ``15\% together.'' These accounts collectively highlight the varied and occasionally synchronous nature of the  INTENTION system's timing in relation to the users' intention.

>>>>

\section{Results}
In the intentional binding task, i.e. the estimation of the time interval between tap and tone, participants generally underestimated the average real delay (350ms) in all three conditions (INTENTION M = 160.3, SD = 116; EXTERNAL M = 176.7, SD = 120.7, AUGMENTED M = 162.6, SD = 118.9). The condition influenced the estimation (${\chi^{2}_{(2)}} = 15.9, p < .001$). In EXTERNAL the estimation was higher compared to INTENTION (beta = 19.2, p < 0.001). Also in EXTERNAL, the estimation was higher compared to AUGMENTED (beta = 18.6, p < 0.001). No difference was observed between INTENTION and AUGMENTED.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/behavioral_results.pdf}
    \caption{(a) Temporal binding effect over conditions. With an average presented time interval of 350ms, lower values in the estimated time interval indicate an underestimation, i.e., temporal binding. (b) Subjective ratings of control across conditions. Significance labels obtained from post-hoc tests on estimated marginal means.}
    \label{fig:results}
\end{figure}

The subjective rating of control differed between conditions (${\chi^{2}_{(2)}} = 35.9, p < .001$). Post-hoc pairwise comparisons revealed that participants rated their motion control higher in INTENTION compared to EXTERNAL (beta = 4.9, p < .0001), and higher in INTENTION compared to AUGMENTED (beta = 3, p < .0001). Further, higher control was observed in AUGMENTED compared to EXTERNAL (beta = 1.9, p = .006).

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/eeg_results.pdf}
    \caption{(a) Grand average event-related potential (ERP) at electrode Cz of pre-movement EEG data epochs preceding the last second before a movement, idle epochs of the same trial are plotted alongside but originate from a different time window, see section~\ref{eeg_methods}; (b) Bottom: Slope features for both idle and pre-movement classes at electrode Cz. Top: Scalp maps of slope values for both classes and all channels. (c): Mean and per participant ROC curves. Dotted line at 15 \% false positive rate indicate the selected threshold for the real-time application.}
    \label{fig:EEG_results}
\end{figure*}

@@

@@

\subsection{Subjective Reports}
Six out of the eight participants made a reference to the source of the EMS in the AUGMENTED condition. In that subgroup, most participants wondered how the system worked, one remarked, ``I can't explain how it works technically.''. They found the stimulation to be sporadic, even during their own actions, leading to a belief that it was coincidental. As one participant put it, ``I have no idea what controlled the stimulation, I think it was coincidence when stimulation occurred.''. Furthermore, participants reported that they found the timing of the stimulation to be unpredictable, with one participant noting, ``Stimulation was random in time.''. Some perceived the stimulation as externally triggered, yet partially responsive to their choices, resulting in a sentiment captured by, ``I think that the stimulation in the third block was partly involuntary, but partly as if it was following my decision / choice.''. One participant briefly considered the involvement of their brain waves in controlling the stimulation, but expressing doubts about this possibility, stating, ``But I don't think that is the case.''.

Some participants reported that the stimulation ``sometimes overlapped with the movement, but not often,'' or, it ``came only rarely.'' Another one noted, ``In a few cases, the stimulation came when I had already started the movement.'' For several participants, this overlap between their actions and the system's response occurred infrequently, with another user noting, ``Once, in the millisecond range between my planned movement and its execution.'' However, for some participants, there were moments of near-perfect synchronization, as described by one participant, ``In 3 cases it happened that my intention to press and the impulse of the device happened simultaneously.'' Another one noted, ``Sometimes it really happened that they overlapped. So that I just started to move, and then the device activated,'' that user estimated an overlap of ``40\%'' while another said [we worked] ``15\% together.'' These accounts collectively highlight the varied and occasionally synchronous nature of the system's timing in relation to the users' intentions.
